Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-11 paper.qmd
Added squares to the positions

highd_error_2d_mnist <- error_df |>
  ggplot(aes(x = tSNE1,
             y = tSNE2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.2) +
  scale_colour_continuous_sequential(palette = "Light Grays") +
  geom_rect(aes(xmin = 0.8, xmax = 0.9, ymin = 0.45, ymax = 0.6),
               fill = "transparent", color = "#e41a1c", linewidth = 0.7) +
  geom_rect(aes(xmin = 0.4, xmax = 0.5, ymin = 0.75, ymax = 0.9),
               fill = "transparent", color = "#377eb8", linewidth = 0.7)  +
  geom_rect(aes(xmin = 0.45, xmax = 0.55, ymin = 0.75, ymax = 0.9),
               fill = "transparent", color = "#4daf4a", linewidth = 0.7)  +
  geom_rect(aes(xmin = 0.55, xmax = 0.65, ymin = 0.75, ymax = 0.9),
               fill = "transparent", color = "#984ea3", linewidth = 0.7) 
  # scale_colour_brewer(
  #   type = "seq",
  #   palette = 1
  # ) #+ 
  # theme(
  #     legend.position = "bottom",
  #     legend.text = element_text(size = 10),          # Increase legend text size
  #     legend.key.size = unit(1, "lines")              # Increase size of legend keys
  # ) +
  # guides(
  #     color = guide_legend(
  #         override.aes = list(size = 2.5, alpha = 1)      # Increase point size and opacity in legend
  #     )
  # ) 
```

>>>>

highd_error_2d_mnist <- error_df |>
  ggplot(aes(x = tSNE1,
             y = tSNE2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.2) +
  scale_colour_continuous_sequential(palette = "Light Grays") +
  geom_rect(aes(xmin = 0.8, xmax = 0.9, ymin = 0.45, ymax = 0.6),
               fill = "transparent", color = "#e41a1c", linewidth = 0.7) +
  geom_rect(aes(xmin = 0.75, xmax = 0.85, ymin = 0.8, ymax = 0.95),
               fill = "transparent", color = "#377eb8", linewidth = 0.7)  +
  geom_rect(aes(xmin = 0.25, xmax = 0.35, ymin = 0.55, ymax = 0.7),
               fill = "transparent", color = "#4daf4a", linewidth = 0.7)  +
  geom_rect(aes(xmin = 0.5, xmax = 0.6, ymin = 0.15, ymax = 0.3),
               fill = "transparent", color = "#984ea3", linewidth = 0.7) 
  # scale_colour_brewer(
  #   type = "seq",
  #   palette = 1
  # ) #+ 
  # theme(
  #     legend.position = "bottom",
  #     legend.text = element_text(size = 10),          # Increase legend text size
  #     legend.key.size = unit(1, "lines")              # Increase size of legend keys
  # ) +
  # guides(
  #     color = guide_legend(
  #         override.aes = list(size = 2.5, alpha = 1)      # Increase point size and opacity in legend
  #     )
  # ) 
```
